Intensity & GC Content Report3
========================================================
### Author: Subhrangshu Nandi
### Date: 2013-09-17

### Background

- Response variable: Fluoroscence Intensity
- Covariates: GC Content, Length of fragment, Stretch factor
- Adjacent fragments share the same error
- All 7,134 groups included in this model
- Outliers are eliminated (& documented for further consideration)

### Model

- 15 groups (or channels) are randomly selected from clean data
- Average 50 molecules per group
- Molecule level random effect added (to control for adjacent fragment similarity)
- Three different models:
  1. OLS (no weights)
  2. Weights based on coverage of fragment location (higher the coverage, higher the weight)
  3. Weights based on variance (higher the variance, lower the weight)

### R-Squares of three models

```{r, include=FALSE}
########################################################################
## Initialize Header file and function library                        ##
########################################################################
FilePath <- '~/RA_Genomics/Project_GC_Content/RScripts_GC_Content/'
DataPath <- '~/RA_Genomics/Project_GC_Content/'
DataPath.Steve <- DataPath
Filename.Header <- paste('~/RScripts/HeaderFile_Nandi.R', sep='')
source(Filename.Header)
source(paste(FilePath, 'fn_Library_GC_Content.R', sep=''))
########################################################################

########################################################################
## Data Input                                                         ##
########################################################################
Filename <- paste(DataPath, 'SamplingOutput.RData', sep='')
load(Filename)

MC_Output <- as.data.frame(MC_Output)
```

```{r, echo=FALSE, fig=TRUE, fig.height=7,fig.width=12,fig.align='center'}
lattice::densityplot(~ ModelA_RSquared + ModelB_RSquared + ModelC_RSquared, 
                     data=MC_Output, type='density', auto.key=TRUE, lty=c(1:3),
                     xlab='Model RSquares', lines=T, lwd=2)
```

- Model A (No weights)
```{r, echo=FALSE}
summary(MC_Output[,c('ModelA_RSquared')])[c(1,3, 4, 6)]
```
- Model B (Weights by coverage of fragment location)
```{r, echo=FALSE}
summary(MC_Output[,c('ModelB_RSquared')])[c(1,3, 4, 6)]
```
- Model C (Weights by variance of fragment location)
```{r, echo=FALSE}
summary(MC_Output[,c('ModelC_RSquared')])[c(1,3, 4, 6)]
```

### Intercept of three models
- Model A (No weights)
```{r, echo=FALSE}
summary(MC_Output[,c('ModelA_Intercept_Beta')])[c(1,3, 4, 6)]
```
- Model B (Weights by coverage of fragment location)
```{r, echo=FALSE}
summary(MC_Output[,c('ModelB_Intercept_Beta')])[c(1,3, 4, 6)]
```
- Model C (Weights by variance of fragment location)
```{r, echo=FALSE}
summary(MC_Output[,c('ModelC_Intercept_Beta')])[c(1,3, 4, 6)]
```

### Beta of GC Content of three models
```{r, echo=FALSE, fig=TRUE, fig.align='center'}
lattice::densityplot(~ ModelA_GC_Content_Beta + ModelB_GC_Content_Beta + ModelC_GC_Content_Beta, 
                     data=MC_Output, type='density', auto.key=TRUE, lty=c(1:3),
                     xlab='Model GC_Content Beta', lines=T, lwd=2)
```

### Beta of GC Content of three models
- Model A (No weights)
```{r, echo=FALSE}
summary(MC_Output[,c('ModelA_GC_Content_Beta')])[c(1,3, 4, 6)]
```
- Model B (Weights by coverage of fragment location)
```{r, echo=FALSE}
summary(MC_Output[,c('ModelB_GC_Content_Beta')])[c(1,3, 4, 6)]
```
- Model C (Weights by variance of fragment location)
```{r, echo=FALSE}
summary(MC_Output[,c('ModelC_GC_Content_Beta')])[c(1,3, 4, 6)]
```

Final Equation
========================================================

$log(Intensity) = 10.7 + 0.20 GC\_Content + Other Factors + \epsilon$

$R^2 = 73\%$
